### 2018-02-11 monograph/thesis/chapters/beautifiers.tex
Added some links of interest on beautifiers.tex
Created the Microsoft/XmlNotepad usage example for beautifying.

>>>>

    \url{https://github.com/r-lib/styler}
    \url{https://github.com/github/linguist}
    \url{https://forum.sublimetext.com/t/auto-align-symbolic/34375}
    \url{https://github.com/Thom1729/SmartIndent}
    \url{https://github.com/wbond/package_control_channel/issues/4310} Write a formatter utility

    With this ObjectBeautifier, we can edit XML files like YAML files, because
    the when we load the XML, we create a copy (the YAML version of the XML) on
    the `.object-beauty` folder which is edited by Sublime Text, and let the
    XML on its original place. Then when we save our YAML copy, we translate it
    to the XML original copy.
    \url{https://github.com/Microsoft/XmlNotepad}
